Using SIMD and SIMT vectorization to evaluate sparse chemical kinetic Jacobian matrices and thermochemical source terms

### 2018-08-09 paper.tex
made all section titles sentence-case

\subsection{Thermochemical Source Terms and Jacobian}
This new version of \texttt{pyJac} is capable of evaluating the thermochemical source-terms for using the constant-pressure (\conp/) or constant-volume (\conv/) assumption\footnote{Note: in this context, the ``constant-pressure'' and ``constant-volume'' assumptions refer to evaluation within a reaction sub-step in the operator splitting scheme, rather than a general constant-pressure or constant-volume reactive-flow simulation.}
In this section, we will outline a brief summary of the system evaluated by \texttt{pyJac}; the supplemental material contains the complete---and lengthy---derivations.

@@

\subsection{Code Generation and Testing Infrastructure}
\label{s:unittest}

@@

\section{Results and Discussion}
\subsection{Testing platforms}
\label{s:test_platforms}

@@

\section{Practical notes on OpenCL Usage}
\label{S:opencl}

>>>>

\subsection{Thermochemical source terms and Jacobian}
This new version of \texttt{pyJac} is capable of evaluating the thermochemical source-terms for using the constant-pressure (\conp/) or constant-volume (\conv/) assumption\footnote{Note: in this context, the ``constant-pressure'' and ``constant-volume'' assumptions refer to evaluation within a reaction sub-step in the operator splitting scheme, rather than a general constant-pressure or constant-volume reactive-flow simulation.}
In this section, we will outline a brief summary of the system evaluated by \texttt{pyJac}; the supplemental material contains the complete---and lengthy---derivations.

@@

\subsection{Code generation and testing infrastructure}
\label{s:unittest}

@@

\section{Results and discussion}
\subsection{Testing platforms}
\label{s:test_platforms}

@@

\section{Practical notes on OpenCL use}
\label{S:opencl}
